### 2019-04-25 manuscript/introduction.tex
ref update

Breeding system shifts---changes in the collection of physiological and morphological traits that determine the likelihood that any two gametes unite---are remarkably common and crucially affect the distribution and amount of genetic variation in populations \citep{stebbins1974, barrett2013}.
In particular, self-incompatibility (SI) causes plants to reject their own pollen, and loss of self-incompatibility, yielding self-compatibility (SC), is one of the most replicated transitions in flowering plant evolution \citep{stebbins1974, igic_2008}.
Previous analyses reported higher rates of diversification for SI than for SC lineages in Solanaceae \citep{goldberg_2010}. 
Similarly, heterostylous SI lineages in Primulaceae seem to diversify faster \citep{devos2014}, as do outcrossing lineages in Onagraceae \citep{freyman_2018}.
Despite consistent inferences of their macroevolutionary role, breeding systems are clearly not the sole trait determining diversification rates, and may exhibit complex interactions with other traits.

>>>>

Breeding system shifts---changes in the collection of physiological and morphological traits that determine the likelihood that any two gametes unite---are remarkably common and crucially affect the distribution and amount of genetic variation in populations \citep{stebbins1974, barrett2013}.
In particular, self-incompatibility (SI) causes plants to reject their own pollen, and loss of self-incompatibility, yielding self-compatibility (SC), is one of the most replicated transitions in flowering plant evolution \citep{stebbins1974, igic_2008}.
Previous analyses reported higher rates of diversification for SI than for SC lineages in Solanaceae \citep{goldberg_2010}. 
Similarly, heterostylous SI lineages in Primulaceae seem to diversify faster \citep{devos2014}, as do outcrossing lineages in Onagraceae \citep{freyman_2019}.
Despite consistent inferences of their macroevolutionary role, breeding systems are clearly not the sole trait determining diversification rates, and may exhibit complex interactions with other traits.

### 2019-04-25 manuscript/results.tex
ref update

When considering breeding system alone (I/C model, \cref{figure:netdivall}C), we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010}.
When a hidden state is included (I/C+A/B model), the large net diversification rate difference persists for one of the hidden states but is removed for the other (\cref{figure:netdivall}D).
Thus, differences in net diversification rates are best explained by both breeding system and an unknown factor \citep[as in Onagraceae;][]{freyman_2018}.
% The transition rate from SI to SC is $q_{IC}=0.3$ for both the I/C and the I/C+A/B models.
The statistical model comparison shows very strong support for including the hidden state (\cref{table:bayesfactors}).

>>>>

When considering breeding system alone (I/C model, \cref{figure:netdivall}C), we found a larger net diversification rate for SI than for SC species, in agreement with \citet{goldberg_2010}.
When a hidden state is included (I/C+A/B model), the large net diversification rate difference persists for one of the hidden states but is removed for the other (\cref{figure:netdivall}D).
Thus, differences in net diversification rates are best explained by both breeding system and an unknown factor \citep[as in Onagraceae;][]{freyman_2019}.
% The transition rate from SI to SC is $q_{IC}=0.3$ for both the I/C and the I/C+A/B models.
The statistical model comparison shows very strong support for including the hidden state (\cref{table:bayesfactors}).
